Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-07-24 exp1/iswc2013.tex
A change from John
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@620 43ef1190-90fd-4dd7-a769-d0121f02b80e

The resulting normal plot is in Figure~\ref{fig:frac32normal}. We see
that only two main effects are significant on a $\alpha = 0.05$ level
according to the Lenth criterion, ``Implement'' is again deemed a
significant improvement, and ``Union'' is deemed significantly the
hardest operation for the query engine. We see that some other points
also deviate from the straight line, but with as few runs as this, the
total variance is great, so no other conclusions can be drawn. We may
use the t-test we used in the previous section, as we have only two
active factors and so we may treat it as a $2^2$ experiment with 8
replications, but the resulting $p = 0.00098$ must be expected with
such a small number of runs and thus higher variance.

>>>>

The resulting normal plot is in Figure~\ref{fig:frac32normal}. We see
that only two main effects are significant on a $\alpha = 0.05$ level
according to the Lenth criterion, ``Implement'' is again deemed a
significant improvement, and ``Union'' is deemed significantly the
hardest operation for the query engine. We see that some other points
also deviate from the straight line, but with as few runs as this, the
total variance is great, so no other conclusions can be drawn. We may
use the t-test we used in the previous section, as we have only two
active factors and so we may treat it as a $2^2$ experiment with 8
replications. The resulting $p = 0.00098$ is still very low, albeit
larger than in the previous experiment. This also explains why there
are so few significant effects, and had to be expected with such a
small number of runs and thus higher variance.
